---
output:
  github_document:
    df_print: kable
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gof4srm

gof4srm provides Kolmogorov-Smirnov test for both time and grouped data, and EIC
(extended information criterion) for software reliability growth models.

## Installation

You can install gof4srm from GitHub with:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("SwReliab/gof4srm")
```

Alternatively, you can use Remote to install Rsrat from GitHub

```{r gh-installation2, eval = FALSE}
install.packages("remotes")
remotes::install_github("SwReliab/gof4srm")
```

## Example 1

This is an example of the estimation of software reliability growth models from a fault data (sys1g). 

```{r example1}
### load library
library(gof4srm)

### load example data
data(dacs)

### grouped data from DACS
sys1g

### Esimate all models
(result <- fit.srm.nhpp(fault=sys1g, selection=NULL))

### Draw the graph 
mvfplot(fault=sys1g, srms=result)

### Draw the graph (dmvf)
dmvfplot(fault=sys1g, srms=result)
```

Perform KS test with the significance level 0.05.

```{r example2}
### KS test
ksres <- lapply(result, ks.srm.test)

### Table for P-value
pvalue <- sapply(ksres, function(x) x$p.value)
data.frame(p.value=pvalue, reject0.05=ifelse(pvalue < 0.05, "*", ""))

### MVF for the models that are passed
mvfplot(fault=sys1g, srms=result[pvalue >= 0.05])

### MVF for the models that are passed
dmvfplot(fault=sys1g, srms=result[pvalue >= 0.05])
```

Compute EIC

```{r example3}
### EIC
eicres <- lapply(result, eic.srm)

### Table for EIC
eic <- sapply(eicres, function(x) x$eic)
eic.lower <- sapply(eicres, function(x) x$eic.lower)
eic.upper <- sapply(eicres, function(x) x$eic.upper)
aic <- sapply(result, function(x) x$aic)
data.frame(aic=aic, eic=eic, eic.lower=eic.lower, eic.upper=eic.upper, ks.p.value=pvalue)
```

## Example 2 (Phase-Type SRGM)

This is an example of the estimation of software reliability growth models from a fault data (sys1g). 

```{r gh-installation3, eval = FALSE}
### Install Rphsrm
install.packages("remotes")
remotes::install_github("SwReliab/Rphsrm")
```

```{r example4}
### load library
library(Rphsrm)

### Esimate several phases
(result <- fit.srm.cph(fault=sys1g, phase=c(10,20,30,40,50), selection=NULL))

### Draw the graph 
mvfplot(fault=sys1g, srms=result)

### Draw the graph (dmvf)
dmvfplot(fault=sys1g, srms=result)
```

Perform KS test with the significance level 0.05.

```{r example5}
### KS test
ksres <- lapply(result, ks.srm.test)

### Table for P-value
pvalue <- sapply(ksres, function(x) x$p.value)
data.frame(p.value=pvalue, reject0.05=ifelse(pvalue < 0.05, "*", ""))

### MVF for the models that are passed
mvfplot(fault=sys1g, srms=result[pvalue >= 0.05])

### MVF for the models that are passed
dmvfplot(fault=sys1g, srms=result[pvalue >= 0.05])
```

Compute EIC

```{r example6}
### EIC
eicres <- lapply(result, eic.srm)

### Table for EIC
eic <- sapply(eicres, function(x) x$eic)
eic.lower <- sapply(eicres, function(x) x$eic.lower)
eic.upper <- sapply(eicres, function(x) x$eic.upper)
aic <- sapply(result, function(x) x$aic)
data.frame(aic=aic, eic=eic, eic.lower=eic.lower, eic.upper=eic.upper, ks.p.value=pvalue)
```
